\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{charter,lipsum}
\setlength{\parindent}{0pt}%
\pagestyle{plain}
\usepackage{textcomp}

\begin{document}

\thispagestyle{empty}
\vspace*{4\baselineskip}

\hfill
\begin{tabular}{l@{}}
  \today \\[\bigskipamount]
  
  1280 Rue Saint-Marc, Apt: 1209\\
  Montreal, H3H 2G1\\
  Phone: 514-431-2331 \\
  Email: mehulprajapati2802@gmail.com\\
  Linkedin: \href{www.linkedin.com/in/mehulmp}{www.linkedin.com/in/mehulmp}
\end{tabular}

\bigskip

\begin{tabular}{@{}l}
 To,\\
 HR Department \\
 Bell Canada\\
 Toronto, Ontario, Canada
\end{tabular}

\bigskip

Dear Recruiter,

\bigskip
I am writing this letter to apply for Customer Operations Business Intelligence Intern Program at Bell Canada. I came to know about this opportunity from a career fair event which I attended at Concordia university. Bell\textquotesingle s BI team optimizes cutting-edge tools and technologies and I would feel highly privileged to be a part your team. I am confident that my work experience as a software
developer would fulfill qualification criteria for this job.\\

I am currently pursuing masters in applied computer science at Concordia university. I have 5 years of industrial experience as an embedded software developer. Now, I want to make a \textbf{career shift} into the world of Business intelligence. To build a solid foundation in machine learning, I have enrolled in subjects related to artificial intelligence. Apart from that, I am building open source machine learning projects on GitHub. Also, I have done online courses of Deep learning and Machine learning on Udacity.\\

Please find enclosed my resume and feel free to call me at 514-431-2331, to arrange a time for an interview. I look forward to hearing from you.
\\

Thank you for considering my application.
\bigskip
\\

Regards, \\Mehul Prajapati

\end{document}