% Mehul_Resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

% Edited it, according to my needs.
\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{fontawesome}
\usepackage{enumitem}

%-----------------------------------------------------------
%Edit these values as you see fit
\definecolor{mygrey}{rgb}{0.86, 0.84, 0.82} % Inner background color of title bars (0 = black, 1 = white)
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
%\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
% Custom commands

% newly added
\newcommand{\lineunder} {
    \vspace*{-20pt} \\
    \hspace*{-3pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}
%-----------------------------------------------------------
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.3in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadinged}[4]{
\begin{tabular*}{7.3in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4}\\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
%---------------------------------------------------
% Name and Websites
%---------------------------------------------------
\textbf{\large Mehul Prajapati}\\
%---------------------------------------------------
% Linkedin
%---------------------------------------------------
{\textbf{Embedded Software Developer}} & {{\faLinkedin} \href{https://www.linkedin.com/in/mehulmp}{linkedin.com/in/mehulmp}}\\
%---------------------------------------------------
% Github
%---------------------------------------------------
{Email:} {mehulprajapati2802@gmail.com} &
{{\faGithub} \href{http://www.github.com/mehul-m-prajapati/}{github.com/mehul-m-prajapati}}\\
{Contact:} {+91-9428123392}
\end{tabular*}
\\
\vspace{0.1in}

%---------------------------------------------------
% Education
%---------------------------------------------------
\resheading{Education}
\setlist[itemize]{leftmargin=5.0mm}
\begin{itemize}
\item
\textbf{Dharmsinh Desai University} \hfill{Nadiad, India}\\
\textit{B.Eng in Electronics and Communication, GPA: 3.3/4} \hfill \textit{July 2008 - May 2012}
\end{itemize}

%---------------------------------------------------
% Professional experience
%---------------------------------------------------
\resheading{Professional Experience (4.3 years)}
\begin{itemize}

\item
	\textbf{Mobile Internet India Pvt Ltd} \hfill{Ahmedabad, India}\\
	\textit{Senior Embedded Engineer} \hfill{Apr 2016 - present}
	\begin{itemize} \vspace{-2mm}
		\resitem{Development of Radius protocol sub-dissectors in wireshark 2.4.0 source code.}
		\resitem{Development of Python scripts to automake tasks.}
	\end{itemize}

\item
	\textbf{Volansys Technologies Pvt Ltd} \hfill{Ahmedabad, India}\\
	\textit{Embedded Software Engineer} \hfill{Oct 2014 - July 2015} 
	\begin{itemize} \vspace{-2mm}
		\resitem{Board Support package porting on ARMv7 based Marvel board.}
	\end{itemize}

\item
	\textbf{eInfochips Pvt Ltd} \hfill{Ahmedabad, India}\\
	\textit{Embedded Software Engineer} \hfill{Jan 2014 - Oct 2014}
	\begin{itemize} \vspace{-2mm}
		\resitem{Evaluation of TI6630K2L board peripherals.}
	\end{itemize}

\item
	\textbf{Matrix Comsec Pvt Ltd} \hfill{Vadodara, India}\\
	\textit{Software Developer} \hfill{Aug 2012 - Jan 2014}
	\begin{itemize} \vspace{-2mm}
		\resitem{Development of new features as per requirements for IP-PBX telecom products.}
	\end{itemize}

\end{itemize}

%---------------------------------------------------
% Technical Skills
%---------------------------------------------------
\resheading{Technical Skills}
\begin{itemize}

    \item \textbf{Programming Languages:} C, Python, Linux Bash Shell, LaTeX, HTML, CSS, XML
    \item \textbf{Databases:} SQLite, MySQL
    \item \textbf{Frameworks/Libraries:} Flask, NumPy, Scikit-learn, Pandas, Matplotlib
    \item \textbf{Linux Programming:} Multithreading, IPC, TCP/IP Socket Programming, Makefile
    \item \textbf{OS:} Linux (Ubuntu), Windows
    \item \textbf{Version Control Systems:} git, svn
    \item \textbf{Bus Protocols:} SPI, I2C, CAN, UART
    \item \textbf{Network Protocols:} HTTP, TCP, UDP, Radius, Syslog, SNMP, SMPP
    \item \textbf{Development boards:} Raspberry Pi, Beaglebone Black, TM4C123, Intel Galileo, NodeMCU ESP8266
    \item \textbf{Software Tools:} Eclipse CDT, Keil $\mu$Vision 4, Code Composer Studio, Visual Studio, PyCharm, Jupyter-Notebook, vim
    \item \textbf{Software Engineering Methods:}: Scrum

\end{itemize}


%---------------------------------------------------
% Other Skills
%---------------------------------------------------
\resheading{Other Skills}
    \begin{itemize}
        \item \textbf{Swimming, Chess:} Active member of sports club
        \item \textbf{Puzzle Solving, Competitive Programming:} Practicing as an independent
    \end{itemize}

        
%---------------------------------------------------
% Achievements & Awards
%---------------------------------------------------
\resheading{Achievements \& Awards}
\begin{itemize}
	\item Got National Merit Scholarship from government of India for achieving excellent grades during under-graduation.
	\item Student Appreciation Award, Torrent Power Ltd.
\end{itemize}

%---------------------------------------------------
% Volunteer
%---------------------------------------------------
\resheading{Volunteer}
\begin{itemize}


\item
	\ressubheading{Stanford Scholar Program}{Remote}{Participant}{Participant, Feb 2017 - present}
	\begin{itemize}
		\resitem{Making research paper accessible to non-researchers.}
	\end{itemize}

\item
	\ressubheading{Python Express}{Remote}{Mentor}{Mentor, Sept 2016}
	\begin{itemize}
		\resitem{Taught basics of Python language to undergraduate students.}
	\end{itemize}
	
\item
	\ressubheading{Mozilla}{Remote}{Firefox Student Ambassador}{Firefox Student Ambassador, July 2016 - present}
	\begin{itemize}
		\resitem{Actively participating in Mozilla community meetups and events.}
	\end{itemize}
	
	
\end{itemize}

%---------------------------------------------------
% MOOCs
%---------------------------------------------------
\resheading{Courses}
    \begin{itemize}
        \item \textbf{edx:}
%---------------------------------------------------
%                       edx
%---------------------------------------------------
        \href{https://www.edx.org/course/embedded-systems-shape-world-utaustinx-ut-6-03x} {Embedded Systems},
        \href{https://courses.edx.org/courses/course-v1:Microsoft+DAT203.3x+5T2016/info}{Applied Machine Learning},
        \href{https://courses.edx.org/courses/course-v1:Microsoft+DAT210x+6T2016/info}{Programming with Python for Data Science},
        \href{https://www.edx.org/course/introduction-computer-science-harvardx-cs50x}{Introduction to Computer Science}
%---------------------------------------------------
%                     Coursera
%---------------------------------------------------                
        \item \textbf{Coursera:}                            \href{https://www.coursera.org/learn/machine-learning}{Machine Learning},
        \href{https://www.coursera.org/learn/web-development/home/welcome}{Introduction to Web Development},
        \href{https://www.coursera.org/learn/learn-to-program}{Learn to Program: The Fundamentals}
%---------------------------------------------------
%                     Other
%---------------------------------------------------                                      
        \item \textbf{Goethe Zentrum:} German language (Level - A2)
    \end{itemize}
%---------------------------------------------------
% Major Projects
%---------------------------------------------------
\resheading{Professional Projects}
\begin{itemize}
\item
    % Project Title
    \textbf{Proprietary Wireshark} (C, TCP/IP Networking)
    
    % Description
    Enhancements of Radius protocol dissector. 
    
    % Tasks done
	\begin{itemize}
	    \resitem{Developed sub-dissectors in wireshark to decode specific parts of the customized Radius protocol.}
	    \resitem{Implemented new display filters of proprietary dissected fields.}
	    \resitem{Maintained Radius protocol states dynamically and showed state information on packet details pane of wireshark GUI.}
	   	\end{itemize}
\item
    % Project Title
    \textbf{Data logger for Maritime (IoT)}
	
	% Description
    Fetching marine sensors' data from CAN bus and sending it over the internet. (C, Linux kernel, SQLite, \href{https://github.com/mehul-m-prajapati/canboat}{canboat})
    
    % Tasks done
	\begin{itemize}
	    \resitem{Ported custom Linux kernel 3.2 on TI AM335x Cortex-A8 based development board.}
	    
	    \resitem{Developed SQLite wrapper utility which manages data in SQLite database.}
	    
	    \resitem{Customized canboat utility which fetches NMEA2000 compliant marine sensor data from CAN bus, decodes it and transmits to the cloud for analysis.}

	\end{itemize}

\item
    % Project Title
    \textbf{Thin client on ARMv7 based development board}
    
    % Description
    A customer wanted to build a dual display package on ARMv7 based board for thin client application. (C, BSP)
    % Tasks done
	\begin{itemize}
	    \resitem{Ported Ubuntu 12.04 file-system and Board Support Package on Marvell PXA2128 SoC based development board.}
	    
	    \resitem{Implemented hot plug HDMI event by using udev rules.}
	    
	\end{itemize}

\item
    % Project Title
    \textbf{Embedded SMS Server}
    
    % Description
    Development of a server to convert the SMS to Email and Email to SMS in the Matrix IP-PBX products. The project involved developing the required features by following SMTP and POP3 protocols. (C, IPC, Makefile)

    % Tasks done
	\begin{itemize}
		\resitem{Developed SMS PDU Encoder and Decoder module by following GSM 3.40 standard.}
		
		\resitem{Developed SMS sender, SMS receiver, SMS delivery and System Timer modules to handle all SMS related activity on the system.}
	  	
	  	\resitem{Customized Syslog and Busybox open source utilities.}

	    \resitem{Developed a wrapper module to encode and decode Unicode characters into UTF-8 format using \href{https://github.com/bnoordhuis/libiconv}{libiconv}.}
        
        \resitem{Developed bash shell scripts and makefiles to cross compile software modules.}
		
	\end{itemize}
	
\item
    % Project Title
    \textbf{IP traffic monitoring using SDN switch}
    
     % Description
     Customizing Zodiac-FX SDN switch firmware to support packet filtering, de-duplication, tagging and aggregation. (SDN, Firmware, C)
     
    % Tasks done
	\begin{itemize}
		\resitem{Developed de-duplication module to remove duplication in real-time by comparing md5hash of Ethernet packets.}
		
		\resitem{Configured HPE VAN SDN controller to do packet filtering and tagging.}
		
    \end{itemize}
    
\item
    % Project Title
    \textbf{Real time IP data traffic accounting}
    
    % Description
    Accounting IP data consumption of users and showing its real time graph on web application. (C, MySQL, TCP/IP Networking, \href{https://github.com/mehul-m-prajapati/pmacct}{PMacct})
	% Tasks done
	\begin{itemize}
	    \resitem{Customized promiscuous mode accounting(PMacct) utility to store accounting data in MySQL database.}
	
	    \resitem{Developed Radius protocol decoder module using raddump library and integrated it into PMacct.}
	    
	    \resitem{Developed an algorithm which maps IMSI with IP address to maintain call states in PMacct.}
	    
	\end{itemize}
	
\item
	% Project Title
	\textbf{GSM Engine Support}
	
	% Description
	This project involved evaluation of various GSM engines and adding support of respective GSM modules to Matrix IP-PBX and GSM Gateway products. (C, Windows)
	
	 % Tasks done
	\begin{itemize}
	    \resitem{Evaluation of GSM engines of different vendors like Quectel, SIMCOM and Sierra Wireless.}
	    
	    \resitem{Modification of existing GSM library code to support tested GSM engines.}
	
	\end{itemize}
	
\item
    % Project Title
   \textbf{Computer Telephony Integration}
    
    % Description
    This project involves the development of TSP (Telephony service provider) driver for Matrix IP-PBX products. (C, Socket programming)
    
    % Tasks done
	\begin{itemize}
	    \resitem{Developed TCP socket client application which encodes and decodes proprietary protocol data.}
	    
	    \resitem{Developed “Windows Registry” module which would add/modify the configuration of any software installed in the windows system.}
	    
	\end{itemize}
	
\end{itemize}

\end{document}